---
title: "[LAST NAME], [FIRST NAME], [STUDENT NUMBER] - Homework 4"
author: "[LAST NAME], [FIRST NAME], [STUDENT NUMBER]"
output: html_document
---

Please read all instructions carefully.  Fill in all fields above (Espicially your student number). To allow this file to be knit, you might need to save it in a new location, as you do not have write permissions in the dropbox folder, and R does not work well with chinese characters.
Do not comment out the lines that produce output.  Check your html file before submission to ensure it has all relevant output.  Ensure all answers are your own words and your own work.  Do not delete anything below these instructions.  Thank you! 



**Question 1A:**
```{r Question 1A}
#INSERT CODE HERE
```

**Question 1B:**
```{r Question 1B}
#INSERT CODE HERE
```

**Question 1C:**
```{r Question 1C}
#INSERT CODE HERE
```

**Question 1D:**
```{r Question 1D}
#INSERT CODE HERE
```

**Question 1E:**
```{r Question 1E}
#INSERT CODE HERE
```

**Question 1F:**
```{r Question 1F}
#INSERT CODE HERE
```

**Question 1G:**
```{r Question 1G}
#INSERT CODE HERE

#Insert 'optPrice' here to display it in the html file
```

**Question 1H:**
```{r Question 1H}
#INSERT CODE HERE


#Insert 'optPrice' here to display it in the html file
```

**Question 1I:**
```{r Question 1I}
#INSERT CODE HERE


#Insert 'optPrice' here to display it in the html file
```



**Question 2A:**
[WRITE ANSWER HERE. 4 SENTENCES MAX]

**Question 2B:**
[WRITE ANSWER HERE. 4 SENTENCES MAX]

**Question 2C:**
[WRITE ANSWER HERE. 4 SENTENCES MAX]
